Clone Overflow: \\ An empirical study of online code clone

### 2016-09-23 latex/stackoverflow.tex

@@

\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
\subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}
\begin{table}[H]
	\centering
	\caption{Classifications of clone creation}
	\label{tab:classification_scheme}
	\begin{tabular}{|c|p{13cm}|}
		\hline 
		Category & Descriptions \\ 
		\hline 
		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
		\hline 
		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
		\hline 
		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
		\\ 
		\hline 
		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
		\\ 
		\hline 
		D & Code is a boiler-plate or IDE auto-generated.
		\\ 
		\hline 
		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
		\\ 
		\hline 
		F & Accidental similarity, false clone \\ 
		\hline 
	\end{tabular} 
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Distribution of classification category A--F according to \textit{good}-match pairs}
	\label{tab:good_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
		\hline
		Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$  & 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
		\hline
		Total   &   8  &   0   &  36   &  8   &   474   &   57   & 81  & 664 \\
		\hline
	\end{tabular} 
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification_new}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$ 
		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									
		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
		\hline
		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
		\hline
	\end{tabular} 
\end{table}

@@

@@

\begin{table}[H]
	\centering
	\caption{Distributions of true positive pairs from the investigation of Qualitas (2013-09-01r)}
	\label{tab:tp_pairs}
	\begin{tabular}{l|r|r|r|r|p{6cm}}
	\hline
	Project		& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
	\hline
	%& \multicolumn{5}{c}{\textit{Not included in the latest version}} \\
	%\hline
	jboss		& 2 	& 	0	& 63 	& 1 & NiCad's failure \\
	db-derby 	& 0 	&	0	& 0		& 0 & NiCad's failure \\
	hadoop		& 191 	& 1 	& 2432 	& 5 & NiCad's failure \\
	hibernate 	& 19 	& 	0	& 11 	& 0 & NiCad's failure \\
	ArgoUML		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	checkstyle	& 0		&	0	& 0		& 0 & NiCad's failure \\
	cayenne		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	geotools	& 0		& 	0	& 0		& 0 & NiCad's failure \\
	jena		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	Vuze		& 0		&	0	& 0		& 0 & NiCad's failure \\
	Compiere	& 127	& 2		& 178	& 8 & No update \\
	axion		& 7		& 	0	& 12	& 0 & No update \\
	c-jdbc		& 66	&	0	& 768	& 0 & No update \\
	colt		& 0		& 	0	& 5		& 0 & No update \\
	columba		& 14	&	0	& 177	& 0 & No update \\
	drawswf		& 0		&	0	& 0		& 0 & No update \\
	fit-java	& 0		& 0		& 2 	& 0 & No update \\
	freecs		& 5		& 0		& 22	& 0 & No update \\
	heritrix	& 16	& 0		& 190 	& 0 & No update \\
	iReport		& 0		& 0 	& 0		& 0 & No update \\
	informa		& 31	& 0 	& 22	& 0 & No update \\
	ivatagroupware	& 0	& 0		& 0		& 0 & No update \\
	jFin		& 15	& 0		& 72	& 0 & No update \\
	jOggPlayer	& 12 	& 0		& 52	& 0 & No update \\
	jasml		& 23	& 0		& 47	& 0 & No update \\
	jext		& 80	& 0		& 85	& 0 & No update \\
	jgraphpad	& 1		& 1		& 55	& 0 & No update \\
	jmoney		& 0		& 0		& 0		& 0 & No update \\
	jparse		& 0		& 0		& 0		& 0 & No update \\
	\hline
	%& \multicolumn{5}{c}{\textit{Included in the latest version}} \\
	%\hline
	freecol		& 1		& 1		& 0		& 0		& \textit{FreeColMenuTest.java} exists with the \textit{createImageIcon()} method. Still can't find the reason why it is not reported. \\		
	aoisrc281	& 0		& 0		& 33	& 33 	& \textit{MovieEncoder.java} (in 2 locations) are missing from the latest version. \\
	findbugs	& 0		& 0		& 2		& 2 	& \textit{UnionBugs.java} has been changed. \\
	jgraph		& 0		& 0		& 3		& 3 	& \textit{HelloWorld.java} has been changed. \\
	\hline
	Total		& 610	& 5		& 4231	& 52 	&\\
	\hline
\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Sankey}
	\caption{Relationships between similar code found from Stackoverflow and Qualitas projects}
	\label{fig:sankey}
\end{figure}

>>>>

\section*{Dataset}
In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{Qualitas}.

@@

\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}

\subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}

\begin{table}[H]
	\centering
	\caption{Classifications of clone creation}
	\label{tab:classification_scheme}
	\begin{tabular}{|c|p{13cm}|}
		\hline 
		Category & Descriptions \\ 
		\hline 
		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
		\hline 
		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
		\hline 
		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
		\\ 
		\hline 
		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
		\\ 
		\hline 
		D & Code is a boiler-plate or IDE auto-generated.
		\\ 
		\hline 
		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
		\\ 
		\hline 
		F & Accidental similarity, false clone \\ 
		\hline 
	\end{tabular} 
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{O}: Distribution of classification category A--F according to \textit{good}-match pairs}
	\label{tab:good_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
		\hline
		Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{O}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$  & 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
		\hline
		Total   &   8  &   0   &  36   &  8   &   474   &   57   & 81  & 664 \\
		\hline
	\end{tabular} 
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{N}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification_new}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$ 
		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									
		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
		\hline
		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
		\hline
	\end{tabular} 
\end{table}

@@

\textbf{Qualitas-N:}

@@

\begin{table}[H]
	\centering
	\caption{Projects that do not have resutls in Qualitas-\textit{N} but do have results in Qualitas-\textit{O}}
	\label{tab:tp_pairs}
	\begin{tabular}{l|r|r|r|r|p{6cm}}
	\hline
	\multirow{2}{*}{Project} & \multicolumn{4}{c|}{Qualitas-\textit{O}} & \multicolumn{1}{c}{Qualitas-\textit{N}} \\ \cline{2-6}
			& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
	\hline
	%& \multicolumn{5}{c}{\textit{Not included in the latest version}} \\
	%\hline
	jboss		& 2 	& 	0	& 63 	& 1 & NiCad's failure \\
	db-derby 	& 0 	&	0	& 0		& 0 & NiCad's failure \\
	hadoop		& 191 	& 1 	& 2432 	& 5 & NiCad's failure \\
	hibernate 	& 19 	& 	0	& 11 	& 0 & NiCad's failure \\
	ArgoUML		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	checkstyle	& 0		&	0	& 0		& 0 & NiCad's failure \\
	cayenne		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	geotools	& 0		& 	0	& 0		& 0 & NiCad's failure \\
	jena		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	Vuze		& 0		&	0	& 0		& 0 & NiCad's failure \\
	Compiere	& 127	& 2		& 178	& 8 & No update \\
	axion		& 7		& 	0	& 12	& 0 & No update \\
	c-jdbc		& 66	&	0	& 768	& 0 & No update \\
	colt		& 0		& 	0	& 5		& 0 & No update \\
	columba		& 14	&	0	& 177	& 0 & No update \\
	drawswf		& 0		&	0	& 0		& 0 & No update \\
	fit-java	& 0		& 0		& 2 	& 0 & No update \\
	freecs		& 5		& 0		& 22	& 0 & No update \\
	heritrix	& 16	& 0		& 190 	& 0 & No update \\
	iReport		& 0		& 0 	& 0		& 0 & No update \\
	informa		& 31	& 0 	& 22	& 0 & No update \\
	ivatagroupware	& 0	& 0		& 0		& 0 & No update \\
	jFin		& 15	& 0		& 72	& 0 & No update \\
	jOggPlayer	& 12 	& 0		& 52	& 0 & No update \\
	jasml		& 23	& 0		& 47	& 0 & No update \\
	jext		& 80	& 0		& 85	& 0 & No update \\
	jgraphpad	& 1		& 1		& 55	& 0 & No update \\
	jmoney		& 0		& 0		& 0		& 0 & No update \\
	jparse		& 0		& 0		& 0		& 0 & No update \\
	\hline
	%& \multicolumn{5}{c}{\textit{Included in the latest version}} \\
	%\hline
	freecol		& 1		& 1		& 0		& 0		& \textit{FreeColMenuTest.java} exists with the \textit{createImageIcon()} method. Still can't find the reason why it is not reported. \\		
	aoisrc281	& 0		& 0		& 33	& 33 	& \textit{MovieEncoder.java} (in 2 locations) are missing from the latest version. \\
	findbugs	& 0		& 0		& 2		& 2 	& \textit{UnionBugs.java} has been changed. \\
	jgraph		& 0		& 0		& 3		& 3 	& \textit{HelloWorld.java} has been changed. \\
	\hline
	Total		& 610	& 5		& 4231	& 52 	&\\
	\hline
\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Sankey}
	\caption{Relationships between similar code found from Stackoverflow and Qualitas files}
	\label{fig:sankey}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Sankey_proj}
	\caption{Relationships between similar code found from Stackoverflow and Qualitas projects}
	\label{fig:sankey}
\end{figure}
